Report

### 2021-07-07 Rmd/report.Rmd
CHILDES frequencies in Barcelona and Oxford (the latter provided by @SiowSerene)

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(role~location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "white") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(role~location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "white") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() +

@@

>>>>

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "white") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "white") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() +

@@

### By location

```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
# plot participants
attrition_location <- attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type)

attrition_location %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +

	attrition_location %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +

	plot_layout(guides = "collect", ncol = 1) &
	scale_y_continuous(labels = percent) &
	coord_flip() &
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 10),
		axis.title = element_blank()
	)
```
